Ages of Planets and Stars Observed by Kepler

### 2024-04-15 paper/ms.tex
plot improvements
ms: add Kepler 411 saga

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{camd_M_G_vs_dr3_bp_rp.pdf}
		}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{camd_M_G_vs_adopted_Teff.pdf}
		}

		\subfloat{
		\includegraphics[width=0.5\textwidth]{st_params_adopted_logg_vs_adopted_Teff.pdf}
		}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{st_params_dr3_phot_g_mean_mag_vs_adopted_Teff.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf CAMD}.
    (todo)
	}
	\label{fig:camd}
\end{figure*}

@@

Kepler~411 is also odd, due to the 58\,day-outer planet.

>>>>

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{st_params_M_G_vs_dr3_bp_rp.pdf}
		}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{st_params_M_G_vs_adopted_Teff.pdf}
		}

		\subfloat{
		\includegraphics[width=0.5\textwidth]{st_params_adopted_logg_vs_adopted_Teff.pdf}
		}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{st_params_dr3_phot_g_mean_mag_vs_adopted_Teff.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf todo}.
	}
	\label{fig:camd}
\end{figure*}

@@

Kepler~411 is also odd, due to the 58\,day-outer planet.
\citet{2019A&A...624A..15S} conducted a transiting timing analysis of the
system, confirming Kepler-411d and argued for the presence of a fourth
non-transiting planet, Kepler-411e, based on the TTVs seen in Kepler-411d and
assuming that the system would be nearly coplanar.
Regarding the stellar age, \citet{2019A&A...624A..15S} used the 
\citet{2007ApJ...669.1167B} relation, which yielded an estimate of 212$\pm$31\,Myr.
However, the star's temperature ($\approx$4900\,K) puts it in a regime where
the Barnes~relation has been known to not fit observations for quite some time
\citep[see][Fig.~9]{2008ApJ...687.1264M}.
Our adopted age of $\approx$780$\pm$170\,Myr agrees with the open cluster
calibrators.
